\section{Architecture}

The application is structured into three modules.
Two additional modules serve to test the agent and document the application.

\subsection{Frontend}

\begin{itemize}
    \item Built using React on the Tauri platform.
    \item Provides powerful interface development tools.
    \item Also provides seamless and lightweight cross-platform native application deployment.
    \item Focus on accessibility and ease of use.
    \item Performs user authentication with an external provider.
\end{itemize}

\subsection{Sidecar}

\begin{itemize}
    \item Frontend is packaged along with a Python FastAPI server that will run alongside the application on the user's device.
    \item This server contains all of the logic to interact with the local file system.
    \item This allows headless usage of the application via HTTP.
\end{itemize}

\subsection{Agent}

\begin{itemize}
    \item Agent is a Python FastAPI server deployed to a trusted execution environment (TEE) on the cloud.
    \item Defines the behaviour of the AI agent using LangGraph.
    \item Uses a configurable LLM provision aggregator called OpenRouter, allowing for flexibility in the selection of the language model and the provider.
    \item After validating the authorization of the user, it invokes the agent, and handles subsequent interactions for frontend tool invocation and passing information.
\end{itemize}

\subsection{Benchmark}

\begin{itemize}
    \item The benchmark directly interacts with the agent module.
    \item Uses a curated dataset of document states along with test user prompts.
    \item Each item is scored on various subjective and objective metrics.
\end{itemize}

\subsection{User guide}

\begin{itemize}
    \item Documentation server.
\end{itemize}
